---
title: "Tidy Tuesday - Week 2"
author: "Grace Hu"
date: "15/03/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(janitor)
library(ggthemes)
library(jsonlite)
```

# Task at hand

For this week, I will be looking at the Bechdel Test data taken from [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-09/readme.md). Upon reading the [FiveThirtyEight](https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/) article that inspired this week's data, I wanted to try and recreate two of the plots included in the article: "The Bechdel Test Over Time" and "Median Budget For Films Since 1990".

```{r getdata, include=FALSE, eval=FALSE, message=FALSE}

# Run this to get the data for the first time.

raw_json <- jsonlite::parse_json(url("http://bechdeltest.com/api/v1/getAllMovies"))

all_movies <- raw_json %>% 
  map_dfr(~as.data.frame(.x, stringsAsFactors = FALSE)) %>% 
  rename(imdb_id = imdbid) %>% 
  tibble()

cleaned_bechdel <- all_movies %>% 
  mutate(title = case_when(
    str_detect(title, ", The") ~ str_remove(title, ", The") %>% paste("The", .),
    TRUE ~ str_replace(title, "&#39;", "’")
  ))

cleaned_bechdel %>% 
  write_csv("raw_bechdel.csv")

# IMDB data ---------------------------------------------------------------


imdb_json <- jsonlite::parse_json(url("https://raw.githubusercontent.com/brianckeegan/Bechdel/master/imdb_data.json"))

all_imdb <- imdb_json %>%
  map_dfr(~as.data.frame(.x, stringsAsFactors = FALSE))

cleaned_imdb <- all_imdb %>% 
  janitor::clean_names() %>% 
  mutate(metascore = parse_number(metascore),
         imdb_rating = parse_number(imdb_rating),
         year = as.integer(year)) %>% 
  mutate(imdb_id = str_remove(imdb_id, "tt")) %>% 
  tibble()

# 538 Data ----------------------------------------------------------------

movies <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/bechdel/movies.csv")

cleaned_movies <- movies %>% 
  mutate(imdb_id = str_remove(imdb, "tt")) 

combo_movies <- cleaned_movies %>% 
  left_join(cleaned_imdb) %>% 
  janitor::clean_names()

combo_movies %>% 
  write_csv("movies.csv")
```

```{r readData, echo=FALSE, include=FALSE}

raw_movies <- read_csv("movies.csv")
raw_bechdel <- read_csv("raw_bechdel.csv")

```

# Challenge 01

Recreating "The Bechdel Test Over Time".

## Data Wrangling

```{r ch_01_data_w}

movies <- raw_movies %>%
  mutate(clean_test = fct_relevel(
    as_factor(clean_test), c("nowomen", "notalk", "men", "dubious", "ok")
  ))

movies_acc <- movies %>%
  mutate(year_acc = as_factor(case_when(
    year >= 1970 & year < 1975 ~ "1970 - '74",
    year >= 1975 & year < 1980 ~ "1975 - '79",
    year >= 1980 & year < 1985 ~ "1980 - '84",
    year >= 1985 & year < 1990 ~ "1985 - '89",
    year >= 1990 & year < 1995 ~ "1990 - '94",
    year >= 1995 & year < 2000 ~ "1995 - '99",
    year >= 2000 & year < 2005 ~ "2000 - '04",
    year >= 2005 & year < 2010 ~ "2005 - '09",
    year >= 2010 & year < 2015 ~ "2010 - '13",
  ))) %>%
  mutate(year_acc = fct_relevel(year_acc, levels(year_acc)[9:1]))

```

## Data Visualization

```{r ch_01_data_v}

ggplot(data = movies_acc, aes(x = year_acc, fill = clean_test)) + 
  geom_bar(position = "fill") +
  scale_fill_brewer(palette="PiYG") +
  scale_y_continuous(labels=scales::percent_format()) +
  labs(
    title = "The Bechdel Test Over Time",
    x = "Year",
    y = "Percentage"
  ) +
  theme_minimal() +
  theme(legend.title=element_blank())
```


# Challenge 02

Recreating "Median Budget For Films Since 1990".

## Data Wrangling 

```{r ch_02_data_w}

budget <- movies %>%
  filter(year >= 1990) %>%
  mutate(clean_test = as_factor(case_when(
    as.character(clean_test) == "dubious" ~ "ok",
    TRUE ~ as.character(clean_test)
  ))) %>%
  mutate(clean_test = fct_rev(fct_relevel(clean_test, "notalk", after=2))) %>%
  group_by(clean_test) %>%
  summarise(median_budget = median(budget) / 1000000)

```

## Data Visualization

```{r ch_02_data_v, fig.width=14, fig.height=6}

ggplot(data = budget, aes(x = clean_test, y = median_budget)) +
  geom_bar(stat = "identity", position="dodge", fill="#0190d4") +
  geom_text(aes(label=median_budget), hjust=-0.3) +
  labs(
    title = "The Bechdel Test Over Time",
    subtitle="2013 dollars",
    x = element_blank(),
    y = element_blank()
  ) +
  scale_x_discrete(labels=c(
    "Fewer than two women",
    "Women don't talk to each other",
    "Women only talk about men",
    "Passes Bechdel Test")) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    text = element_text(size=18)
  ) +
  coord_flip()


```
