---
title: "Tidy Tuesday - Week 4"
author: "Grace Hu"
date: "01/04/2021"
output: html_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggthemes)
```

# Task at hand

For this week, I will be looking at the Makeup data taken from [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-30/readme.md). As someone who has an interest in beauty and makeup, I know that race representation in the cosmetics industry has been a problem. In the recent years, more and more companies are aware that shade range in foundation products is very important, but I wanted to explore that further with the data.

```{r getdata, include=FALSE, message=FALSE}

# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2021-03-30')

```

```{r readData, echo=FALSE, include=FALSE}

shades_raw <- tuesdata$allShades

```

# Challenge 01

For the first task, I want to mimic the plots found in the [related article](https://pudding.cool/2021/03/foundation-names/). However, I did not know how to colour every individual data point with the given HEX codes, so I looked online for some references. I found some helpful [code](https://github.com/florencevdubois/MyTidyTuesdays/blob/master/code/2021.03.30.R) from Florence V. Dubois' GitHub repository and learned some new features of `ggplot`!

## Data Wrangling

```{r ch_01_data_w}

shades_cat <- shades_raw %>%
  mutate(l_cat = floor(lightness * 20), UID = as.factor(row_number())) %>%
  group_by(l_cat) %>%
  mutate(num = row_number()) %>% 
  ungroup()


shades_cat_colours <- shades_cat$hex

```

## Data Visualization

```{r ch_01.1_data_v, dpi=300}

ggplot(data = shades_cat, aes(x=l_cat, y = num)) +
  geom_raster(aes(fill = UID)) +
  scale_fill_manual(values = shades_cat_colours) +
  scale_x_discrete() +
  labs(
    title = "Foundation shade ranges",
    subtitle="from all makeup companies at Sephora and Ulta"
  ) +
  theme_void() +
  theme(legend.position="",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) 

```

# Challenge 02

Now, I am interested in seeing what the foundation range is like for any collections with 20 or less shades.

## Data Wrangling 

```{r ch_02_data_w}

shades_bot_20 <- shades_cat %>%
  group_by(brand, product) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  filter(count <= 20) %>%
  group_by(l_cat) %>%
  mutate(num = row_number()) %>%
  ungroup()


shades_bot_20_colours <- shades_bot_20$hex

```

## Data Visualization

```{r ch_02_data_v, fig.width=14, fig.height=6, dpi=300}

ggplot(data = shades_bot_20, aes(x=l_cat, y = num)) +
  geom_raster(aes(fill = UID)) +
  scale_fill_manual(values = shades_bot_20_colours) +
  scale_x_discrete() +
  labs(
    title = "Foundation shade ranges",
    subtitle="from foundation collections with 20 or less shades at Sephora and Ulta"
  ) +
  theme_void() +
  theme(legend.position="",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) 


```
