---
title: "Tidy Tuesday - Week 3"
author: "Grace Hu"
date: "23/03/2021"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggthemes)
```

# Task at hand

For this week, I will be looking at the Video Game data taken from [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-16/readme.md). For the first task, I want to look at the data for my favourite video game, Stardew Valley. For the second task, I want to look at the top 5 games played in 2020 (ignoring missing-ness).

```{r getdata, include=FALSE, message=FALSE}

# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2021-03-16')

games <- tuesdata$games
```

```{r readData, echo=FALSE, include=FALSE}

games_cleaned <- games %>%
  mutate(date = as.Date(str_c(year, month, "01", sep=" "), "%Y %B %d"))

```

# Challenge 01

Stardew Valley Stats (one of my favourite video games!)

## Data Wrangling

```{r ch_01_data_w}

stardew_data <- games_cleaned %>%
  filter(gamename == "Stardew Valley")


```

## Data Visualization

```{r ch_01.1_data_v}

ggplot(data = stardew_data, aes(x = date, y = avg)) +
  geom_area(stat = "identity", fill = "#151152", alpha=0.8) +
  labs(
    title = "Average number of Stardew Valley players over time",
    x = "Date",
    y = "Avg number of players"
  ) +
  theme_minimal()

```

# Challenge 02

Top 5 games in 2020 (released before 2020)

## Data Wrangling 

```{r ch_02_data_w}

game_release_date <- games_cleaned %>%
  filter(is.na(gain)) %>%
  arrange(date) %>%
  distinct(gamename, .keep_all = TRUE) %>%
  mutate(release_date = date) %>%
  select(gamename, release_date)

top_game_names <- games_cleaned %>%
  left_join(game_release_date, by="gamename") %>%
  filter(year == 2020 & release_date <= as.Date("2020-01-01")) %>%
  group_by(gamename) %>%
  mutate(avg_2020 = mean(avg)) %>%
  arrange(-avg) %>%
  distinct(gamename) %>%
  head(n=5)

top_games <- games_cleaned %>%
  filter(year == 2020 & gamename %in% top_game_names$gamename)

```

## Data Visualization

```{r ch_02_data_v, fig.width=14, fig.height=6}

ggplot(data = top_games, aes(x = date, fill = gamename)) +
  geom_area(aes(y = avg), alpha=0.6) +
  labs(
    title = "Top 5 Games in 2020",
    subtitle="By highest average number of players over the year",
    x = "Date",
    y = "Avg number of players"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette="Dark2")

```
